\large \texttt{insectDisease}: programmatic access to the \textit{Ecological Database of the World's Insect Pathogens}

### 2022-01-05 manuscript/manuscript.tex
zenodo info added to manuscript

\paragraph*{FAIR data}
The FAIR principles represent guidelines for making data more persistent, findable, and well-documented. Structuring the data as an R package ensures that metadata and data are packaged together, where R manual files contain column names and data descriptions for each data product (\textit{Findable}). All code to take data from the raw data (\texttt{data-raw} folder) to the end product .RData and .csv files is contained in the versioned R data package, and integration with Zenodo provides a DOI for each release (\textit{Accessible}). Apart from providing data in these multiple formats, user access is aided by structuring the data as a package in a very popular computing language among biologists (and other folks too) and providing all code for data processing and serving in an open and public-facing repository (\textit{Interoperable}). Having all code and data in a streamlined, open, and versioned format, serving the data through an interactive web portal, and publishing this software note collectively serve to promote the use of this data resource (\textit{Reusable}).

@@

\subsection*{Data accessibility}
The \texttt{insectDisease} R package is currently available on GitHub \\ (github.com/viralemergence/insectDisease), with `.csv' files in the csv directory for long-term data stability. GitHub releases of the data ensure versioning is maintained and all versions are accessible. At the time of this writing, the current version is 1.1.0 (available at \\ \texttt{https://github.com/viralemergence/insectDisease/releases/tag/1.1.0}).

>>>>

\paragraph*{FAIR data}
The FAIR principles represent guidelines for making data more persistent, findable, and well-documented. Structuring the data as an R package ensures that metadata and data are packaged together, where R manual files contain column names and data descriptions for each data product (\textit{Findable}). All code to take data from the raw data (\texttt{data-raw} folder) to the end product .RData and .csv files is contained in the versioned R data package, and integration with Zenodo (\texttt{https://doi.org/10.5281/zenodo.5821896}) provides a DOI for each release (\textit{Accessible}). Apart from providing data in these multiple formats, user access is aided by structuring the data as a package in a very popular computing language among biologists (and other folks too) and providing all code for data processing and serving in an open and public-facing repository (\textit{Interoperable}). Having all code and data in a streamlined, open, and versioned format, serving the data through an interactive web portal, and publishing this software note collectively serve to promote the use of this data resource (\textit{Reusable}).

@@

\subsection*{Data accessibility}
The \texttt{insectDisease} R package is currently available on GitHub \\ (github.com/viralemergence/insectDisease), with `.csv' files in the csv directory for long-term data stability. GitHub releases of the data ensure versioning is maintained and all versions are accessible. At the time of this writing, the current version is 1.2.0 (available at \\ \texttt{https://github.com/viralemergence/insectDisease/releases/tag/1.2.0}). Releases are given a DOI through integration with Zenodo (\texttt{https://doi.org/10.5281/zenodo.5821896}).
